Covariate analysis of CMC RNASeq data reprocessed with RSEM-feature counts workflow with GRCh38 (ACC with CQN normalisation)

### 2018-10-04 code/Rmd/CMC_ACC_RSEM_GRCh38_CQN_ModSel.Rmd
modified first code block

---
title: "Covariate analysis of CMC RNASeq data reprocessed with RSEM-feature counts workflow with GRCh38 (DLPFC with CQN normlaisation)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)

@@

knit2synapse::createAndKnitToFolderEntity(file = "./CMC_DLPFC_RSEM_GRCh38_CQN_ModSel.Rmd",
                                          parentId ="syn9846623",
                                          folderName = 'DLPFC - RSEM - EXPECTED COUNTS - GRCh38 - CQN - Sparse Model')
```

>>>>

---
title: "Covariate analysis of CMC RNASeq data reprocessed with RSEM-feature counts workflow with GRCh38 (ACC with CQN normalisation)"
author: "Kelsey Montgomery"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)

@@

knit2synapse::createAndKnitToFolderEntity(file = "./CMC_ACC_RSEM_GRCh38_CQN_ModSel.Rmd",
                                          parentId ="syn9846623",
                                          folderName = 'ACC - RSEM - EXPECTED COUNTS - GRCh38 - CQN - Sparse Model')
```
